Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-20 writeup/gz_hubble_data.tex
Comment on weighting for anonymous users. Closes #81.
added reference to toms thesis

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the image as seen on screen.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions or 
individual classifier ability and skill. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters intended to capture the bulk of the change in bias: the
$i$-band surface brightness ($\mu_i$; intrinsic) and redshift ($z$;
extrinsic).

@@

Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
galaxies relative to their lowest simulated redshift. In this analysis, only
galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were
used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
surface brightness measurements in \sextractor; this includes 3,950 of the
total 6,466 images. For each simulated redshift value \zsim{} at a fixed
surface brightness $\mu$, \ffeaturesz, the value measured at that simulated
redshift, is plotted against \ffeaturesrest, the value measured for the same
galaxy at \zsim$=0.3$.

>>>>

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions or 
individual classifier ability and skill. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters intended to capture the bulk of the change in bias: the
$i$-band surface brightness ($\mu_i$; intrinsic) and redshift ($z$;
extrinsic).

@@

Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
galaxies relative to their lowest simulated redshift. In this analysis, only
galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were
used (see Table \ref{tbl:ferengivalues}), and only those which had detectable
surface brightness measurements in \sextractor~\citep{mel16}; this includes 3,950 of the
total 6,466 images. For each simulated redshift value \zsim{} at a fixed
surface brightness $\mu$, \ffeaturesz, the value measured at that simulated
redshift, is plotted against \ffeaturesrest, the value measured for the same
galaxy at \zsim$=0.3$.
